\documentclass[12pt]{amsart}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{tgtermes}

\newcommand{\ssection}[1]{\noindent\textbf{#1}\vspace{.2cm}}
\newcommand{\esection}{\vspace{.3cm}}

\newcommand{\svs}{\vspace{.1cm}}

\begin{document}
\vfill

% Title
\begin{center}
{\Large\textbf{Matthew Badger}} \vspace{.2cm}\\
{\large Curriculum Vitae} \vspace{.2cm}\\
\textsf{www.math.uconn.edu/$\sim$badger} \vspace{.2cm}\\
\textsf{matthew.badger@uconn.edu} \vspace{.4cm}

\end{center}

\vfill

\ssection{Employment and Visiting Positions}

\textsc{University of Connecticut}

\begin{itemize}
\item Assistant Professor, Department of Mathematics, Fall 2014 -- \emph{present}
\end{itemize}

\svs

\textsc{Stony Brook University} \begin{itemize}
\item James H. Simons Instructor, Department of Mathematics, Fall 2011 -- Spring 2014.
\end{itemize}

\svs

\textsc{Visiting Positions}

\begin{itemize}
\item PCMI, Harmonic Analysis, July 2018.
\item MSRI, Harmonic Analysis, January -- March 2017.
\item IPAM, Interactions Between Analysis and Geometry, March -- June 2013.
\end{itemize}

\esection

\vfill

\ssection{Education}

\noindent \textsc{University of Washington} \begin{itemize}
\item Ph.D. in Mathematics, August 2011. \quad\emph{Thesis advisor}: Tatiana Toro.
\item M.S. in Mathematics, August 2008.
\end{itemize} \vspace{.1cm}

\noindent \textsc{University of Pittsburgh} \begin{itemize}
\item B.S. in Mathematics, April 2006.
\item B.A. in Political Science, April 2006.
\end{itemize}

\esection

\vfill

\ssection{Research Interests}

\noindent My main research focus is on the \textbf{Geometry of Sets and Measures} that appear in various types of classical analysis. I am especially interested in problems from geometric measure theory and in higher-dimensional (3D+) analogues of geometric function theory in the complex plane (2D). \svs

\noindent\textsc{Buzzwords} \svs

\noindent\emph{Geometric Measure Theory, Rectifiable Measures, Elliptic PDE in Rough Domains},

\hfill \emph{Harmonic Measure}, \emph{Modulus of Curves and Measures}, \textsc{and} \emph{Quasiconformal Mappings}

\esection

\vfill

\ssection{Grants and Fellowships}

\begin{itemize}
\item NSF 1650546, ``CAREER: Analysis and Geometry of Measures", 2017--2022, \$410,000\svs
\item NSF 1500382, ``Geometry of Sets and Measures", 2015--2018, \$120,000 \svs
\item NSF Mathematical Sciences Postdoctoral Research Fellowship, 2012--2015, \$150,000 \svs
\item RTG Graduate Fellowship, Inverse Problems \& PDE, University of Washington,\par 2009--2010 and 2010--2011. \svs
\item VIGRE Graduate Fellowship, University of Washington, 2006--2007.
%\item M.M. Culver Award, University of Pittsburgh, 2004, 2005 and 2006: prize awarded annually to outstanding undergraduates majoring in mathematics.
\end{itemize}

\esection

\newpage\ssection{Thesis Students}

\begin{itemize}

\item Lisa Naples, currently 4th year graduate student at UConn, passed General Exam 12/2017

\end{itemize}

\esection

\ssection{Postdoctoral Fellows}

\begin{itemize}

\item Murat Akman, Evarist Gine Postdoctoral Fellow at UConn, 2016--present

\item Vyron Vellis, Postdoctoral Fellow at UConn, 2016--present

\end{itemize}

\esection


\ssection{Publications}

\begin{enumerate}
\item[1.] Harmonic polynomials and tangent measures of harmonic measure, \emph{Rev.~ Mat.~ Iberoam.} \textbf{27} (2011), no.~ 3, 841--870. \textsf{arXiv:0910.2591}
\item[2.] Null sets of harmonic measure on NTA domains: Lipschitz approximation revisited, \emph{Math.~ Z.} \textbf{270} (2012), no.~ 1--2, 241--262. \textsf{arXiv:1003.4547}
\item[3.] Flat points in zero sets of harmonic polynomials and harmonic measure from two sides, \emph{J.~ London Math.~ Soc.}~ \textbf{87} (2013), no.~ 1, 111--137. \textsf{arXiv:1109.1427}
\item[4.] (with James T. Gill, Steffen Rohde and Tatiana Toro) Quasisymmetry and rectifiability of quasispheres, \emph{Trans.~ Amer.~ Math.~ Soc.} \textbf{366} (2014), no.~ 3, 1413--1431. \textsf{arXiv:1201.1581}
\item[5.] Beurling's criterion and extremal metrics for Fuglede modulus, \emph{Ann.~ Acad.~ Sci.~ Fenn. Math.} \textbf{38} (2013), 677--689.
 \textsf{arXiv:1207.5277}
\item[6.] (with Raanan Schul) Multiscale analysis of 1-rectifiable measures: necessary conditions, \emph{Math. Ann.} \textbf{361} (2015), no.~ 3--4, 1155--1172. \textsf{arXiv:1307.0804}
\item[7.] (with Jonas Azzam and Tatiana Toro) Quasiconformal planes with bi-Lipschitz pieces and extensions of almost affine maps, \emph{Adv.~ Math.} \textbf{275} (2015), 195--259. \textsf{arXiv:1403.2991}
\item[8.] (with Stephen Lewis) Local set approximation: Mattila-Vuorinen type sets, Reifenberg type sets, and tangent sets, \emph{Forum Math.~ Sigma} \textbf{3} (2015), e24, 63 pp. \textsf{arXiv:1409.7851}
\item[9.] (with Raanan Schul) Two sufficient conditions for rectifiable measures, \emph{Proc.~Amer. Math. Soc.} \textbf{144} (2016), no.~6, 2445-2454. \textsf{arXiv:1412.8357}
\item[10.] (with Murat Akman, Steve Hofmann, and Jos\'e Mar\'ia Martell) Rectifiability and elliptic measures on 1-sided NTA domains with Ahlfors-David regular boundaries. \emph{Trans. Amer. Math. Soc.} \textbf{369} (2017), no.~ 8, 5711--5745. \textsf{arXiv:1507.02039}
\item[11.] (with Max Engelstein and Tatiana Toro) Structure of sets which are well approximated by zero sets of harmonic polynomials, \emph{Anal. PDE}. \textbf{10} (2017), no.~ 6, 1455--1495.  \textsf{arXiv:1509.03211}
\item[12.] (with Raanan Schul) Multiscale analysis of 1-rectifiable measures II: characterizations. \emph{Anal. Geom. Metr. Spaces} \textbf{5} (2017), no.~1, 1--39. \textsf{arXiv:1602.03823}
\end{enumerate}\vspace{.1cm}

\textsc{Accepted for Publication}
\begin{enumerate}
\item[13.] (with Vyron Vellis) Geometry of measures in real dimensions via H\"older parameterizations. To appear in \emph{J. Geom. Anal.} \textsf{arXiv:1706.07846}
\end{enumerate}\vspace{.1cm}

\textsc{Preprints}
\begin{enumerate}
\item[14.] Generalized rectifiability of measures and the identification problem. Preprint, submitted. \textsf{arXiv:1803.10022}
%\item[15.]  Preprint. 2017.
\end{enumerate}\vspace{.1cm}

\textsc{In Preparation}

\begin{enumerate}
\item[15.] (with Max Engelstein and Tatiana Toro) Regularity of the singular set in a two-phase problem for harmonic measure with H\"older data.
\item[16.] (with Lisa Naples and Vyron Vellis) H\"older curves and parameterizations in the Analyst's Traveling Salesman theorem
\end{enumerate}
%\end{enumerate}

\esection

\ssection{Plenary Talks}

\begin{itemize}
\item ``Open Problems about Curves, Sets, and Measures". 8th Ohio River Analysis Meeting. Lexington, Kentucky. March 2018.
\end{itemize}

\esection

\ssection{Other Invited Research Talks}

\begin{itemize}

\item AMS special session on Analysis and Geometry in Non-smooth Spaces. Eastern Sectional Meeting. Boston, Massachusetts. April 2018.
\item AMS special session on Regularity of PDEs in Rough Domains. Eastern Sectional Meeting. Boston, Massachusetts. April 2018.
\item AMS special session on Analysis at the Intersection of Geometric Measure Theory and Partial Differential Equations. Western Sectional Meeting. Portland, Oregon. April 2018.
\item Analysis and PDE seminar. University of Kentucky. Lexington, Kentucky. March 2018.
\item 3rd Northeast Analysis Network Meeting. Syracuse, New York. September 2017.
\item Geometric Measure Theory conference. Warwick, United Kingdom. July 2017.
\item Harmonic analysis seminar. MSRI. Berkeley, California. March 2017.
\item Conference on ``Analysis on Metric Spaces." University of Pittsburgh. March 2017.
\item Analysis seminar. Brown University. Providence, RI. October 2016.
\item Analysis and PDE seminar. University of Cincinnati. Cincinnati, Ohio. April 2016.
\item Rainwater seminar. University of Washington. Seattle, Washington. March 2016.
\item Analysis and probability seminar. University of Connecticut. Storrs. March 2016.
\item AMS Special Session on Analysis and Geometry in Nonsmooth Metric Measure Spaces. Joint Mathematics Meetings. Seattle, Washington. January 2016.
\item Minisymposiam, ``New Trends in Elliptic and Parabolic PDEs" SIAM conference---Analysis of PDE. Scottsdale, Arizona. December 2015.
\item Rainwater seminar. University of Washington. Seattle, Washington. May 2015.
\item Analysis seminar. Brown University. Providence, Rhode Island. April 2015.
\item Analysis seminar. University of Missouri. Columbia, Missouri. April 2015.
\item Colloquium. Worcester Polytechnic Institute. Worcester, Massachusetts. March 2015.
\item Geometry seminar. University of Jyv\"askyl\"a. Jyv\"askyl\"a, Finland. February 2015.
\item Geometric analysis seminar. University of Helsinki. Helsinki, Finland. February 2015.
\item Analysis seminar. Fordham University. Bronx, New York. November 2014.
\item Ahlfors-Bers Colloquium VI. Yale University. New Haven, Connecticut. October 2014.
\item Analysis and probability seminar. University of Connecticut. Storrs. September 2014.
\item Dynamical systems seminar. Stony Brook University and the Institute for Mathematical Sciences. Stony Brook, New York. May 2014.
\item Colloquium. University of Connecticut. Storrs, Connecticut. January 2014.
\item Rainwater seminar. University of Washington. Seattle, Washington. January 2014.
\item Analysis seminar. University of Illinois, Urbana-Champaign. November 2013.
\item Analysis seminar. Syracuse University. Syracuse, New York. October 2013.
\item AMS Special Session on Harmonic Analysis and Partial Differential Equations.\\ Louisville, Kentucky. October 2013.
\item AMS Special Session on Analysis, Dynamics and Geometry in and around Teichm\"uller spaces. Ames, Iowa. April 2013.
\item Analysis seminar. Temple University. Philadelphia, Pennsylvania. February 2013.
\item Complex analysis seminar. University of Washington. Seattle. January 2013.
\item Perspectives in HA, GMT, and PDE, and their applications to SCV. Temple University. Philadelphia, Pennsylvania. September 2012.
\item Simons Postdoctoral Fellows Meeting. Simons Center for Geometry and Physics. Stony Brook, New York. April 2012.
\item Complex analysis seminar. University of Washington. Seattle. January 2012.
\item Dynamical systems seminar. Stony Brook University and the Institute for Mathematical Sciences. Stony Brook, New York. September 2011.
\item AMS Special Session on Geometric Aspects of Analysis and Measure Theory. Eastern Sectional Meeting. Ithaca, New York. September 2011.
\item AMS Special Session on Harmonic Analysis and PDE. Joint Mathematics Meetings. New Orleans, Louisiana. January 2011.
\item Analysis seminar. Brown University. Providence, RI. December 2010.
\item Harmonic analysis seminar. Universit\'e Paris-Sud XI. Orsay, France. April 2010.
\item Rainwater seminar. University of Washington. Seattle, Washington. February 2010.
\item Harmonic analysis conference. Centre de Recerca Matem\`atica (CRM). Bellaterra, Spain. June 2009.
\item Rainwater seminar. University of Washington. Seattle, Washington. May 2009.
\end{itemize}

\textsc{Upcoming Invited Talks}
\begin{itemize}

\item Rainwater seminar. University of Washington. Seattle, Washington. May 2018.
\item AMS special session on Harmonic Analysis and PDE. Southeastern Sectional Meeting. Fayetteville, Arkansas. November 2018.

\end{itemize}

%\vspace{.25cm}

\esection

%\ssection{Conference and Workshop Participation}
%
%\begin{itemize}
%\item AMS Central Sectional Meeting. Ames, Iowa. April 2013.
%\item Interactions between Analysis and Geometry. Institute for Pure and Applied Mathematics (IPAM). Los Angeles, California. March - June 2013.
%\item Joint Mathematics Meetings. San Diego, California. January 2013.
%\item Perspectives in HA, GMT, and PDE, and their applications to SCV. Temple University. Philadelphia, Pennsylvania. September 2012.
%\item Mathematics Research Communities: PDE, Harmonic Analysis, Complex Analysis and Geometric Measure Theory. Snowbird, Utah. June 2012.
%\item Simons Postdoctoral Fellows Meeting. Simons Center for Geometry and Physics. Stony Brook, New York. April 2012.
%\item AMS Eastern Sectional Meeting. Ithaca, New York. September 2011.
%\item Geometric measure theory and its applications. Mathematical Sciences Research Institute (MSRI). Berkeley, CA. July 2011.
%\item Free boundary problems: theory and applications. Mathematical Sciences Research Institute (MSRI). Berkeley, CA. January 2011.
%\item Joint Mathematics Meetings. New Orleans, Louisiana. January 2011.
%\item Analysis and boundary value problems on real and complex domains. Banff International Research Station (BIRS). Banff, Alberta. July 2010.
%\item Harmonic analysis and its applications: a conference in honor of Richard Wheeden. Universidad de Sevilla. Sevilla, Spain. June 2010.
%\item Harmonic analysis, geometric measure theory and quasiconformal mappings. Centre de Recerca Matem\`atica (CRM). Bellaterra, Spain. June 2009.
%\item Four advanced courses on quasiconformal mappings, PDE and geometric measure theory. Centre de Recerca Matem\`atica (CRM). Bellaterra, Spain. June 2009.
%\item Quantitative and computational aspects of metric geometry. Institute for Pure and Applied Mathematics (IPAM). Los Angeles, California. January 2009.
%\item Quasiconformal mappings and analysis on metric spaces: a conference in memory of Juha Heinonen. University of Michigan. Ann Arbor, Michigan. May 2008.
%\end{itemize}
%
%\esection


\ssection{Invited Mini Courses}


\begin{itemize}
\item \emph{Introduction to Geometry of Sets and Measures}, 3 lectures, $4\frac12$ hours. Progress in\\ Harmonic Analysis and Geometric Measure Theory. Temple University. April 2014.
\end{itemize}
\esection

\ssection{Professional Activities}

\begin{itemize}
\item Organizer of ``Geometric and Harmonic Analysis: a Conference for Graduate Students". University of Connecticut. March 2019. Co-organized with Murat Akman, Vyron Vellis.
\item Organizer of ``Nonsmooth Analysis: a Workshop for Postdocs". University of Connecticut. November 2017. Website at:
\texttt{http://nonsmooth2017.math.uconn.edu/}
\item Co-organizer (with Vasileios Chousionis): AMS Special Session in Geometric Aspects of Harmonic Analysis. Fall Eastern Sectional Meeting. Brunswick, Maine. September 2016.
\item Co-organizer (with Chris Bishop and Raanan Schul): AMS Special Session in Geometric Measure Theory and Its Applications. Spring Eastern Sectional Meeting. Stony Brook, New York. March 2016.
\item Chair of organizing committee for the UConn Special Semester in Nonsmooth Analysis. University of Connecticut. Department of Mathematics. Fall 2015. Co-organized with Vasileios Chousionis, Masha Gordina, Luke Rogers, and Sasha Teplyaev.
\item Co-organizer (with Jim Gill and Joan Lind): AMS Special Session in Complex Analysis, Probability and Metric Geometry. Spring Southeastern Sectional Meeting. Knoxville, Tennessee. March 2014.
\item Co-organizer (with Theresa Anderson, Nathan Pennington, Eric Stachura): AMS Special Session in Harmonic Analysis, PDE, and Geometric Measure Theory. Joint Mathematics Meetings. San Diego. January 2013.
\item TA for Summer Graduate Courses in Geometric Measure Theory. MSRI. July 2011.
\item Organized a series of ``Professional Development Sessions" for the  mathematics graduate students at University of Washington, 2010 -- 2011.
\item Served on 2 NSF Review Panels
\item Refereed papers for multiple journals, including

 $\rhd$ Ann. Sci. \'Ec. Norm. Sup\'er. \ $\rhd$ Duke Math. J. \ $\rhd$ Geom. Func. Anal.

 $\rhd$ Invent. Math. \ $\rhd$ J. Amer. Math. Soc. \ $\rhd$ J. Anal. Math.

  $\rhd$ J. Eur. Math. Soc. (JEMS) \ $\rhd$ J. Geom. Anal. \  $\rhd$ Nonlinear Anal.

  $\rhd$ Proc. Amer. Math. Soc. \ $\rhd$ Rev. Mat. Iberoamericana
\item Reviewer for \emph{Mathematical Reviews}, 27 reviews, 2012--2017.
\end{itemize}

\esection

\ssection{Teaching Experience}

\noindent \textsc{University of Connecticut}\vspace{.1cm}

\textsf{Graduate Courses}
\begin{itemize}
\item Math 5010\ \ \ \ Topics in Analysis: Geometric Measure Theory\hfill\textbf{Fall 2018}
\item Math 5111\ \ \ \ Measure Theory \& Integration\hfill \textbf{Spring 2018}
\item Math 5120\ \ \ \ Complex Analysis \hfill \textbf{Spring 2016}
\item Math 5110\ \ \ \ Introduction to Modern Analysis \hfill \textbf{Fall 2015}
\item Math 5110\ \ \ \ Introduction to Modern Analysis \hfill\textbf{Fall 2014}

\end{itemize} \vspace{.1cm}


\textsf{Undergraduate Courses -- Math Majors}
\begin{itemize}

\item Math 3150\ \ \ \ Analysis I\hfill\textbf{Fall 2017}

\item Math 3150\ \ \ \ Analysis I\hfill\textbf{Fall 2016}

\item Math 4110\ \ \ \ Introduction to Modern Analysis \hfill\textbf{Fall 2015}

\item Math 4110\ \ \ \ Introduction to Modern Analysis \hfill\textbf{Fall 2014}

\end{itemize} \vspace{.1cm}

\textsf{Undergraduate Courses -- Service Courses}
\begin{itemize}
\item Math 2410\ \ \ \ Elementary Differential Equations\hfill\textbf{Fall 2016}
\item Math 2410\ \ \ \ Elementary Differential Equations\hfill\textbf{Spring 2016}
\item Math 1131\ \ \ \, Calculus I \hfill \textbf{Summer 2015}
\end{itemize} \vspace{.2cm}

\noindent \textsc{Stony Brook University}\vspace{.1cm}

\textsf{Graduate Courses} \begin{itemize}
\item Math 550 Real Analysis II \hfill \textbf{Spring 2014}
\item Math 638 Topics in Real Analysis: {\small Brownian Motion and Harmonic Measure} \hfill \textbf{Fall 2013}
\end{itemize}

\vspace{.1cm}

\textsf{Undergraduate Courses -- Math Majors}\begin{itemize}
\item Math 322 Analysis in Several Dimensions \hfill \textbf{Spring 2012}
\end{itemize}

\vspace{.1cm}

\textsf{Undergraduate Courses --- Service Courses}\begin{itemize}
\item Math 211 Introduction to Linear Algebra \hfill \textbf{Fall 2012}
\item Math 125 Calculus A (Differential Calculus) \hfill \textbf{Fall 2011}
\item Math 126 Calculus B (Integral Calculus) \hfill \textbf{Fall 2011}
\end{itemize}
\vspace{.2cm}

%\noindent In Fall 2012, I also directed separate independent studies by two undergraduate math majors on (i) Harmonic Function Theory, (ii) Analysis on Manifolds. \vspace{.2cm}

\newpage\noindent \textsc{University of Washington}\vspace{.1cm}

\textsf{Undergraduate Courses --- Service Courses}\begin{itemize}
\item Math 309 Linear Analysis \hfill \textbf{Fall 2010}
\item Math 308 Matrix Algebra with Applications \hfill \textbf{Winter 2010}
\item Math 308 Matrix Algebra with Applications \hfill \textbf{Summer 2008}
\end{itemize}

%\noindent\emph{Grader}\\
%Graded coursework for graduate and senior undergraduate courses, held weekly office hours.\begin{itemize}
%\item Math 524-525-526 Real Analysis \hfill \textbf{Fall 2008 - Spring 2009}
%\item Math 424-425-426 Fundamental Concepts of Analysis \hfill \textbf{Fall 2007 - Spring 2008}
%\end{itemize}\vspace{.05cm}

%\noindent\emph{Teaching Assistant}\\
%Led small group sections twice a week, held weekly office hours, graded exams.\begin{itemize}
%\item Math 124 Calculus I\hfill \textbf{Fall 2006}
%\end{itemize}\vspace{.05cm}

%\noindent\textsc{University of Pittsburgh}\vspace{.1cm}

%\noindent\emph{Teaching Assistant}\\
%Designed, presented and graded five MATLAB ``exploration assignments" for sophomore level course in linear algebra required for engineering students. \begin{itemize}
%\item Math 0280 Introduction to Matrices and Linear Algebra\hfill \textbf{Spring 2006}
%\end{itemize}

\esection

\thispagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\lhead{\footnotesize \arabic{page}}
\lfoot{}
\cfoot{}
\rfoot{\footnotesize \emph{Last updated on April 24, 2018.}}

\end{document}
